Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-03-16 msc-publication.tex
add more conclusions to terrain-following advection

\begin{itemize}
	\item l2 error is $\sim 10 \times$ worse on SLEVE compared to BTF
	\item \TODO{find out what results are for cut cell grid}
	\item Conclusions/summary for this test
\end{itemize}

>>>>

\begin{itemize}
	\item l2 error is $\sim 10 \times$ worse on SLEVE compared to BTF, slightly worse again on cut cell grid
	\item Conclusions/summary: Accuracy depends upon alignment of flow with grid.  Accuracy not reduced by grid distortions.  Accuracy on BTF grid comparable with accuracy on SLEVE grid in horizontal advection test.
\end{itemize}
